Convective heat transport in stratified atmospheres at low and high Mach number

### 2016-09-09 tex/nusselt_paper.tex
gets "good" rought drafts of 1st/2nd/part of 3rd section in.

%\documentclass[iop]{emulateapj}
\documentclass[aps, prl, twocolumn, groupedaddress]{revtex4-1}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{color}
\usepackage{bm}
\usepackage{empheq}
\usepackage{natbib}
\usepackage{cancel}
\usepackage[colorlinks=True, linkcolor=blue, citecolor=blue]{hyperref}
\usepackage[all]{hypcap}

@@

\newcommand{\Div}[1]{\ensuremath{\nabla\cdot\left( #1\right)}}
\newcommand{\angles}[1]{\ensuremath{\left\langle #1 \right\rangle}}
\newcommand{\grad}{\ensuremath{\nabla}}
\newcommand{\RB}{Rayleigh-B\'{e}nard }
\newcommand{\stressT}{\ensuremath{\bm{\bar{\bar{\Pi}}}}}

@@

\begin{abstract}
Here we study the effects of varying the strength of buoyant driving (the Rayleigh number, Ra) and the
characteristic flow speed (the Mach number, Ma) on convective heat transport in stratified atmospheres.
We utilize polytropic reference states to condition the Mach number and study the evolution of the
non-dimensional Nusselt number (Nu) as Ra is increased in various Ma regimes.
\end{abstract}
\maketitle

%%%%% Body of the paper
\section{Introduction \label{section:intro}}
Convection is ubiquitous among natural systems such as stellar envelopes and planetary atmospheres.
In these systems, compressibility and buoyancy couple to produce complex effects which are not seen in
the widely-studied \RB convection.
Early studies of stratified
convection in two \cite{graham1975, chan&all1982, hurlburt&all1984, cattaneo&all1990} and three 
\cite{malagoli&all1990, cattaneo&all1991, brummell&all1996} dimensions
utilized polytropically stratified atmospheres, in which the equation of hydrostatic equilibrium is satisfied
under the assumptions of constant gravitational acceleration, thermal diffusivity and a linear temperature profile.
radiative transfer properties (cite some papers), the polytrope is a particularly useful reference state for
stratified convection studies.

Aside from the physical size of the domain in which convection occurs, \RB convection has two main control
parameters.  These are the non-dimensional Rayleigh number (Ra, the ratio of buoyanty driving to diffusivity)
and the Prandtl number (Pr, the ratio of viscous to thermal diffusivity).  In stratified atmospheres, Ra
and Pr combine with the degree of stratification of the atmosphere and the characteristic Mach number of
motions in the convective flows.  While there have been numerous studies of the effects of varying
Ra, Pr, and atmospheric stratification (cite some), there are few studies of the effects of Mach number
on the resulting heat transport properties of the resulting convection.

In this letter, we hold the Prandtl number and density stratification constant in polytropic atmospheres.
We examine the effects of varying the Rayleigh number and characteristic superadiabaticity of the reference
polytrope as a means of probing dynamics at low and high Mach number.  We utilize the non-dimensional
Nusselt number to study the heat transport characteristics at low and high Mach number.

\section{Model \& Equations \label{section:model}}
We study a fluid whose equation of state is that of an ideal gas, $P = R^*\rho T$ and whose
initial stratification is polytropic.
The primary assumptions utilized in constructing a polytropic atmosphere are that the gravitational
acceleration and conductive heat flux are invariant throughout the depth of the atmosphere. In order
to satisfy the latter assumption, the thermal conductivity, $\kappa$ and temperature gradient
$\grad T_0$ are often taken as constants, such that, \bm{$F}_{\text{cond}} = -\kappa \grad T_0 = \text{constant}$.
Under these assumptions, solving the equation of hydrostatic equilibrium produces an atmosphere defined by
\begin{equation}
\begin{split}
\rho_0(z) &= \rho_{00}(z_0 - z)^m \\
T_0(z)    &= T_{00}(z_0 - z)
\label{eqn:polytrope}
\end{split}
\end{equation}
and $z$ increases upwards within the bounds $z =\{0, L_{z}\}$.
We specify the number of density scale heights the atmosphere spans, $n_\rho$ to determine $L_{z}$. Throughout
this study, we set $n_{\rho} = 3$ such that the density at the bottom of the atmosphere is larger
than that at the top of the atmosphere by roughly a factor of 20.
Thermodynamic variables are nondimensionalized at the top of the atmosphere as 
$P_0(L_z) = \rho_0(L_z) = T_0(L_z) = 1$, requiring $z_0 \equiv L_z + 1$ and $R^* = T_{00} = \rho_{00} = 1$.  
The polytropic index is set by the adiabatic index of a monatomic ideal gas, $\gamma = 5/3$ and the 
superadiabatic excess \cite{graham1975}, $\epsilon$, such that $m = (\gamma - 1)^{-1} - \epsilon = m_{ad} - \epsilon$ 
and the subsequent entropy gradient at the top of the atmosphere is $\grad S(L_z) = -\epsilon$,
the negative value of the superadiabatic excess.  We argue that the characteristic timescale of such an
atmosphere is related to the characteristic atmospheric buoyancy time, $t_{\text{b}} = \sqrt{L_z/g\epsilon}$,
not the characteristic thermal diffusion time, $t_{\text{th}} = L_z^2/\chi$.

Atmospheric diffusivities are set by the Rayleigh number and the Prandtl number.  We define the
non-dimensional Rayleigh number as
\begin{equation}
\text{Ra} = \frac{g L_z^3 (\Delta S_0 / c_P)}{\nu\chi},
\end{equation}
where $\Delta S_0$ is the entropy difference between the top and bottom of the atmosphere, 
$\nu$ is the kinematic viscosity (viscous diffusivity), and $\chi$ is the thermal dififusivity.  
The relationship between the thermal and viscous diffusivities is
set by the Prandtl number, Pr$ = \nu/\chi$.   We relate the dynamic viscosity, $\mu$ and the thermal conductivity,
$\kappa$, to their corresponding diffusivities such that 
$\nu \equiv \mu/\rho$ and $\chi \equiv \mu/\rho$.  As a result, $\text{Ra} \propto (\nu\chi)^{-1} \propto
\rho^2$, such that for our atmospheres with $n_{\rho} = 3$, the Rayleigh number increases by a factor of
approximately 400 from the top of the domain to the bottom of the domain.  Such a formulation leaves Pr
constant throughout the depth of the atmosphere, and in this paper we specifically study $\text{Pr} = 1$.

At the constant values of $n_\rho$ and Pr used, the primary control parameters of convection are $\epsilon$
and Ra.  We decompose our atmosphere into the background polytrope ($\rho_{0}, T_{0}$) and the fluctuations
about that background ($\bm{u}, \rho_{1}, T_{1}$).  The scaling of the entropy gradient with $\epsilon$
is reflected in the evolved values of these fluctuations, which follow the scaling of
Ma$^{1/2} \propto T_1/T_0 \propto \rho_{1}/\rho_{0} \propto \epsilon$, and which scale as roughly $Ra^{0.3}$,
see Fig. \ref{fig:ma_v_eps}.

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/ma_v_eps.png}
\caption{Shown are characteristic mach numbers from IVPs spanning six decades of $\epsilon$, from
very low Mach number to near Mach one.  A very strong Ma $\propto \epsilon^{1/2}$ relation is clear. 
\label{fig:ma_v_eps} }
\end{figure}

We start with initial conditions of random small perturbations compared to $\epsilon$ in the temperature
field.  We evolve the Fully Compressible Navier-Stokes equations with an energy-conserving energy equation,
which take the form:
\begin{align}
&\begin{aligned}
&\frac{D \ln\rho}{D t} + \Div{\bm{u}} = 0
	\label{eqn:continuity_eqn}
\end{aligned}\\
&\begin{aligned}
&\rho\frac{D\bm{u}}{D t}=
-\grad P + \rho\bm{g} - \nabla\cdot\stressT
	\label{eqn:momentum_eqn}
\end{aligned}\\
&\begin{aligned}
\rho c_V\left(\frac{D T}{D t} + (\gamma-1)T\Div{\bm{u}}\right) + &\Div{-\kappa\grad T} = \\
&-\left(\stressT\cdot\nabla\right)\cdot\bm{u} 
	\label{eqn:energy_eqn}
\end{aligned}
\end{align}
where $D/Dt \equiv \partial_t + \bm{u}\cdot\grad$ and the viscous stress tensor is defined as
\begin{equation}
\Pi_{ij} \equiv -\mu\left(\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i} - \frac{2}{3}\delta_{ij}\Div{\bm{u}}\right).
	\label{eqn:stress_tensor}
\end{equation}

In such stratified systems, the total convective flux can be defined as
\begin{equation}
\bm{F}_{\text{conv}} = \bm{F}_{\text{enth}} + \bm{F}_{\text{KE}} + \bm{F}_{\text{PE}} + \bm{F}_{\text{visc}},
\end{equation}
where $\bm{F}_{\text{enth}} \equiv \rho\bm{u}(c_V T + P/\rho)$ is the enthalpy flux, $\bm{F}_{\text{KE}} \equiv 
\rho|\bm{u}|^2\bm{u}$ is the kinetic energy flux, $\bm{F}_{\text{PE}} \equiv \rho\bm{u}\phi$ is the potential
energy flux (with $\phi \equiv -gz$), 
and $\bm{F}_{\text{visc}} \equiv \bm{u}\cdot\stressT$ is the viscous flux.  Dotting 
Eq. \ref{eqn:momentum_eqn} with $\bm{u}$ and adding it to 
Eq. \ref{eqn:energy_eqn}, we retrieve the full energy equation in conservation form,
\begin{equation}
\frac{\partial}{\partial t}\left(\rho\left[\frac{|\bm{u}|^2}{2} + c_V T + \phi\right]\right) +
\Div{\bm{F}_{\text{conv}} + \bm{F}_{\text{rad}}} = 0
	\label{eqn:energy_eqn_full}
\end{equation}
where $\bm{F}_{\text{rad}} = -\kappa \grad T$.

The efficiency of convection is defined by the Nusselt number.  While the Nusselt number is well-defined in \RB convection
as the amount of total flux divided by the steady-state background conductive flux 
\cite{johnston&doering2009, otero&all2002},
a well-defined Nusselt number is more elusive in stratified convection.  A traditional definition of the Nusselt
number in stratified convection is \cite{graham1975,hurlburt&all1984}
\begin{equation}
N \equiv \frac{F_{\text{conv, z}} + F_{\text{rad, z}} - F_A}{F_{\text{ref}} - F_A},
\label{eqn:nusselt}
\end{equation}
where $F_{\text{conv, z}}$ and $F_{\text{rad, z}}$ are the z-components of $\bm{F}_{\text{conv}}$ and $\bm{F}_{\text{rad}}$,
respectively.  $F_A$ is the adiabatic conductive flux, defined as $F_A = -\kappa \grad T_{\text{ad}}$.  For an
atmosphere in hydrostatic equilibrium, such as a polytrope, $\grad T_{\text{ad}} \equiv - g / c_{P}$, and thus
$F_A = \kappa g / c_{P}$.  $F_{\text{ref}} = \Delta T / L_z$ is the conductive flux of a linear profile connecting the upper
and lower plates, where $\Delta T = T_{u} - T_{\ell}$.

Such a definition of the Nusselt number is general to both stratified and \RB convection.  Convection works to
suppress entropy stratification and create isentropic atmospheres.  Under the Boussinesq approximation where
density variations are ignored, entropy stratification is directly proportional to temperature stratification,
such that $\grad S \rightarrow 0$ only when $\grad T \rightarrow 0$.  Thus, for \RB convection, 
$\grad T_{\text{ad}} \equiv 0$ and the familiar form of $N$ is retrieved.  In the case of stratified convection,
as $\epsilon \rightarrow m_{ad} + 1$, as in \cite{brandenburg&all2005}, $\grad P \propto g \rightarrow 0$ and
the resulting $\grad T_{\text{ad}} \rightarrow 0$.  In such a case, $F_A \rightarrow 0$ and the familiar
definition of the \RB nusselt number is appropriate to use. However, for any given values of $\epsilon$, including
the very small values used in this work, Eq. \ref{eqn:nusselt} is the proper non-dimensional definition
of the Nusselt number.

We utilize the novel Dedalus pseudospectral framework (cite website?) to time-evolve Eqs. 
\ref{eqn:continuity_eqn}-\ref{eqn:energy_eqn}.  We use a dealiased Chebyshev (vertical)
and Fourier (horizontal) grid in which the
physical grid dimensions are 3/2 the size of the coefficient grid.  Our coefficient grid sizes range from
64x256 grid points (low Ra) to 768x3072 grid points (Ra = $10^{7.66}$).  The atmosphere is bounded above
and below by impenetrable, stress free, fixed temperature boundary conditions such that
\begin{equation}
w = \partial_z u = T_1 = 0
\end{equation}
at the boundaries.  Theh domain is horizontally periodic.

\section{Results \label{section:results}}

We ran initial value problems for a few hundreds of buoyancy times past the convective transients from 
Rayleigh numbers around $R_{crit}$ up to Rayleigh numbers of $\approx 10^7 R_{crit}$ (BOOTSTRAPPING?).  At
high values of $\epsilon$, shock systems form in the upper atmosphere near downflow lanes 
(see e.g. Fig. \ref{fig:entropy_snapshots}b) and propagate towards upflow lanes.  Such systems were reported in
both two \cite{cattaneo&all1990} and three \cite{malagoli&all1990} dimensional polytropic simulations previously.
Low mach number flows, such as those on an $\epsilon = 10^{-4}$ atmosphere (e.g. Fig. \ref{fig:entropy_snapshots}a)
have similar bulk thermodynamic structure but lack the complicating dynamics of shock heating.

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/snapshots_fig.png}
\caption{Two characteristic snapshots after about 200 buoyancy times are shown at $\epsilon=10^{-4}$ (top)
and $\epsilon=0.5$ (bottom) at Ra = $10^6$.  
\label{fig:entropy_snapshots} }
\end{figure}

@@

\begin{figure}[b]
\includegraphics[width=3.4375in]{./figs/fluxes_fig.png}
\caption{Flux profiles for low (top) and high (bottom) Mach number flows.  
\label{fig:flux_profiles} }
\end{figure}

At low Rayleigh number, diffusivities are high and the flows are very laminar.  Such flows often achieve a
steady state and have a well-defined Nusselt number which is independent of time.  However, as the Rayleigh
number increases, the flows become increasingly time-dependent.  Even steady structures such as solid
``rolls'' like those pictured in Fig. \ref{fig:entropy_snapshots} have highly time-dependent Nusselt numbers.
This is, in part, due to the fact that cold downdrafts floating to the bottom of the domain can be entrained
by upflows, or warm risen parcels can be entrainedi n the intense cold downdrafts.  Such events reverse the
preferred direction of flux in the system, and even let the Nusselt number become negative for short periods of
time.  See Fig. \ref{fig:nu_v_time}.  As a result, it is necessary to take a long time average of the fluxes
before calculating the Nusselt number at higher Rayleigh number. (IS THIS USEFUL?)

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/nu_v_time.png}
\caption{The evolution of the Nusselt number is shown at low ($10^2$) and high ($10^7$) Rayleigh number and at
$\epsilon = 10^{-4}$.  At low Rayleigh number, the system is able to settle into a time invariant solution. As
the Rayleigh number is raised, the thermodynamic structure become increasingly complex and time variant, and a
time-average of the Nusselt number is required to obtain a sensible mean.
\label{fig:nu_v_time} }
\end{figure}

@@

\begin{acknowledgements}
This work was supported by the CU/NSO Hale Graduate Fellowship and Juri's allocation and Ben's allocation.
\end{acknowledgements}

>>>>

%\documentclass[iop]{emulateapj}
\documentclass[aps, prl, twocolumn, groupedaddress, amsfonts, amssymb, amsmath]{revtex4-1}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{natbib}
%\usepackage[colorlinks=True, linkcolor=blue, citecolor=blue]{hyperref}
%\usepackage[all]{hypcap}

@@

\newcommand{\Div}[1]{\ensuremath{\nabla\cdot\left( #1\right)}}
\newcommand{\angles}[1]{\ensuremath{\left\langle #1 \right\rangle}}
\newcommand{\grad}{\ensuremath{\nabla}}
\newcommand{\RB}{Rayleigh-B\'{e}nard }
\newcommand{\stressT}{\ensuremath{\bm{\bar{\bar{\Pi}}}}}
\newcommand{\nrho}{\ensuremath{n_{\rho}}}

@@

\begin{abstract}
Here we study stratified convection in the context of polytropically stratified atmospheres. 
We hold the density stratification and Prandtl number (Pr) constant while studying the dependence
of the Nusselt number (Nu), which quantifies the efficiency of convective heat transport, on
variations of the Mach number (Ma) and the Rayleigh number (Ra).  In the low Ra regime, high and
low Ma flows have very different scalings of Nu with Ra.  In the high Ra regime, high and low Ma flows
have nearly the same scaling of Nu with Ra, with power laws near (enter here), reminiscent of the
Nu $\propto$ Ra$^{2/7}$ seen in \RB convection.
\end{abstract}
\maketitle

%%%%% Body of the paper
\section{Introduction}
\refstepcounter{section}
\label{sec:intro}
Convection is essential to heat transport in the cores of high mass stars, the
envelopes of low mass stars, and the atmospheres of terrestrial and jovian planets. In such systems, convection
occurs in the presence of the atmospheric stratification, which can be small but extends up to 
14 density scale heights in the Sun's convective envelope.
Clearly a basic understanding of the
properties of compressible convection in stratified media is important to understanding systems in astrophysics
and planetary sciences.  Unfortunately, most attempts to learn about the properties of convection in these
systems were overshadowed or muddied by additional attempts to make numerical models that include all of the
complexities of the real system.  As such, we know little about the fundamental properties of stratified convection.

Some of the earliest numerical experiments on stratified convection
were performed in both two \cite{graham1975, chan&all1982,
hurlburt&all1984, cattaneo&all1990} and three \cite{cattaneo&all1991, brummell&all1996} dimensions and
revealed a number of basic properties in the moderate-to-high Mach number regime.
Unlike the widely-studied \RB convection, in which upflows and downflows are symmetrical, highly stratified
convection exhibits high-velocity, narrow downflow lanes and slow, broad upflow lanes.  As velocities approach
the speed of sound, shocks begin to form near the downflow lanes at the top of the atmosphere and propagate toward the upflows.
In \RB convection, the temperature gradient
and by proxy the radiative flux approach zero in the convecting region.  In stratified convection, the 
\emph{entropy} gradient is flattened by convection, but this does not necessitate the disappearance of the
radiative flux due to contributions of thermodynamic variables other than temperature to the entropy.

In \RB convection, there exist two primary control parameters: the Rayleigh number (Ra), the ratio of
buoyant driving to diffusive damping, and the Prandtl number (Pr), the ratio of viscous to thermal
diffusivity.  Along with the aspect ratio of the physical domain, these two numbers entirely control the
dynamics of the convection.  In stratified atmospheres, in addition to specifying the equation of state and
fundamental properties of the gas, the two control parameters of \RB convection are joined by the degree of
stratification across the domain and the characteristic Mach number (Ma) of the convective flows.  
Polytropically stratified atmospheres, such as those used in early studies, are an ideal extension of
\RB convection into the stratified realm as the two additional control parameters are directly linked to
basic properties of the atmosphere.  The density stratification is set by the number of density scale heights
the atmosphere spans (\nrho), and the Mach number is controlled by the superadiabatic excess ($\epsilon$),
which is the deviation of the polytropic index from that of an adiabatic polytropic index \cite{graham1975}.

In this letter, we study the effects of variations of $\epsilon$ and Ra on the heat transport of convection
in polytropically stratified atmospheres, characterized by the Nusselt number (Nu).  We hold \nrho and Pr
constant across all simulations and examine moderate (4) and large (8) aspect ratios.  In section 
\ref{sec:experiment}, we describe the construction of atmospheres, our equations, and our method for
numerical time evolution.  We describe our findings in section \ref{sec:results} and discuss
implications in section \ref{sec:discussion}.

\section{Experiment} 
\refstepcounter{section}
\label{sec:experiment}
We study a fluid composed of monatomic ideal gas particles, with an adiabatic index of $\gamma = 5/3$ and
whose equation of state is $P = R^*\rho T$. 
The initial stratification is polytropic, such that the gravitational
acceleration and conductive heat flux are invariant throughout the depth of the atmosphere. In order
to satisfy the latter assumption, the thermal conductivity, $\kappa$ and temperature gradient
$\grad T_0$ are often taken as constants, such that $\bm{F}_{\text{cond,0}} = -\kappa \grad T_0 = \text{constant}$.
Under these assumptions, solving the equation of hydrostatic equilibrium produces an atmosphere defined by
\begin{equation}
\begin{split}
\rho_0(z) &= \rho_{00}(z_0 - z)^m \\
T_0(z)    &= T_{00}(z_0 - z),
\label{eqn:polytrope}
\end{split}
\end{equation}
where $z$ increases upwards within the bounds $z =\{0, L_{z}\}$.
We specify the number of density scale heights the atmosphere spans, $n_\rho$, to determine $L_{z}$. Throughout
this letter, we set $n_{\rho} = 3$ such that the density at the bottom of the atmosphere is larger
than at the top by a factor of 20.
Thermodynamic variables are nondimensionalized at the top of the atmosphere as 
$P_0(L_z) = \rho_0(L_z) = T_0(L_z) = 1$, requiring $z_0 \equiv L_z + 1$ and $R^* = T_{00} = \rho_{00} = 1$.  
The polytropic index is set by the adiabatic index and the
superadiabatic excess, $\epsilon$, such that $m = m_{ad} - \epsilon$
where $m_{ad} \equiv (\gamma-1)^{-1}$ is the adiabatic polytropic index.
The subsequent entropy gradient at the top of the atmosphere is $\grad S(L_z) = -\epsilon$,
the negative of the superadiabatic excess.  We argue that the characteristic timescale of such an
atmosphere is not only linked to the characteristic thermal diffusion time, $t_{\text{th}} = L_z^2/\chi$,
but is also related to the characteristic atmospheric buoyancy time, $t_{\text{b}} = \sqrt{L_z/g\epsilon}$.
We will utilize buoyancy time units throughout this letter.

Atmospheric diffusivities are set by the Rayleigh number and the Prandtl number.  We define the
non-dimensional Rayleigh number as
\begin{equation}
\text{Ra} = \frac{g L_z^3 (\Delta S_0 / c_P)}{\nu\chi},
\end{equation}
where $\Delta S_0$ is the entropy difference between the top and bottom of the atmosphere, 
$\nu$ is the kinematic viscosity (viscous diffusivity), and $\chi$ is the thermal dififusivity.  
The relationship between the thermal and viscous diffusivities is
set by the Prandtl number, Pr$ = \nu/\chi$.   We relate the dynamic viscosity, $\mu$, and the thermal conductivity,
$\kappa$, to their corresponding diffusivities such that 
$\nu \equiv \mu/\rho$ and $\chi \equiv \mu/\rho$.  As a result, $\text{Ra} \propto (\nu\chi)^{-1} \propto
\rho^2$, such that for our atmospheres with $n_{\rho} = 3$, the Rayleigh number increases by a factor of
400 from the top of the domain to the bottom of the domain.  Such a formulation leaves Pr
constant throughout the depth of the atmosphere, and in this letter we impose $\text{Pr} = 1$.

At the constant values of $n_\rho$ and Pr used, the primary control parameters of convection are $\epsilon$
and Ra.  We decompose our atmosphere into the background polytrope ($\rho_{0}, T_{0}$) and the fluctuations
about that background ($\bm{u}, \rho_{1}, T_{1}$).  The scaling of the entropy gradient with $\epsilon$
is reflected in the evolved values of these fluctuations, which follow the scaling of
Ma$^{1/2} \propto T_1/T_0 \propto \rho_{1}/\rho_{0} \propto \epsilon$, and which scale as roughly $Ra^{0.3}$,
as in Fig. \ref{fig:ma_v_eps}.

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/ma_v_eps.png}
\caption{Figure (a) shows characteristic horizontally averaged maximum mach numbers which have been
time averaged over 100$t_{b}$ starting 60$t_{b}$ after the start of IVP simulations. At low $\epsilon$,
Ma shows a power law slope of 0.5048 and 0.5129 at Ra = $10^2$ and $10^5$, respectively (need err bars).
When $\epsilon \rightarrow m_{ad}$, large deviations from this power law are seen and the system quickly
approaches Ma $\approx 1$.  Ma shows weak scaling with $\epsilon$, and does not exceed Ma$ \approx 1$
\label{fig:ma_v_eps} }
\end{figure}

We evolve the Fully Compressible Navier-Stokes equations,
which take the form:
\begin{align}
&\begin{aligned}
&\frac{D \ln\rho}{D t} + \Div{\bm{u}} = 0
	\label{eqn:continuity_eqn}
\end{aligned}\\
&\begin{aligned}
&\rho\frac{D\bm{u}}{D t}=
-\grad P + \rho\bm{g} - \nabla\cdot\stressT
	\label{eqn:momentum_eqn}
\end{aligned}\\
&\begin{aligned}
\rho c_V\left(\frac{D T}{D t} + (\gamma-1)T\Div{\bm{u}}\right) + &\Div{-\kappa\grad T} = \\
&-\left(\stressT\cdot\nabla\right)\cdot\bm{u} 
	\label{eqn:energy_eqn}
\end{aligned}
\end{align}
where $D/Dt \equiv \partial_t + \bm{u}\cdot\grad$ and the viscous stress tensor is defined as
\begin{equation}
\Pi_{ij} \equiv -\mu\left(\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i} - \frac{2}{3}\delta_{ij}\Div{\bm{u}}\right).
	\label{eqn:stress_tensor}
\end{equation}

In such stratified systems, the total convective flux can be defined as
\begin{equation}
\bm{F}_{\text{conv}} \equiv \bm{F}_{\text{enth}} + \bm{F}_{\text{KE}} + \bm{F}_{\text{PE}} + \bm{F}_{\text{visc}},
\end{equation}
where $\bm{F}_{\text{enth}} \equiv \rho\bm{u}(c_V T + P/\rho)$ is the enthalpy flux, $\bm{F}_{\text{KE}} \equiv 
\rho|\bm{u}|^2\bm{u}$ is the kinetic energy flux, $\bm{F}_{\text{PE}} \equiv \rho\bm{u}\phi$ is the potential
energy flux (with $\phi \equiv -gz$), 
and $\bm{F}_{\text{visc}} \equiv \bm{u}\cdot\stressT$ is the viscous flux.  Taking an inner product of
Eq. \ref{eqn:momentum_eqn} with $\bm{u}$ and adding it to 
Eq. \ref{eqn:energy_eqn}, the full energy equation in conservation form is retrieved,
\begin{equation}
\frac{\partial}{\partial t}\left(\rho\left[\frac{|\bm{u}|^2}{2} + c_V T + \phi\right]\right) +
\Div{\bm{F}_{\text{conv}} + \bm{F}_{\text{rad}}} = 0
	\label{eqn:energy_eqn_full}
\end{equation}
where $\bm{F}_{\text{rad}} = -\kappa \grad T$.  An understanding of the flux terms is essential to characterizing
the convective heat transport in our systems.

The atmosphere is bounded above
and below by impenetrable, stress free, fixed temperature boundary conditions such that
\begin{equation}
w = \partial_z u = T_1 = 0
\end{equation}
at the boundaries.

We utilize the novel Dedalus pseudospectral framework (cite website?) to time-evolve Eqs. 
\ref{eqn:continuity_eqn}-\ref{eqn:energy_eqn} using a fourth-order Runge-Kutta timestepping scheme.  
Variables are time-evolved on a dealiased Chebyshev (vertical)
and Fourier (horizontal, periodic) domain in which the
physical grid dimensions are 3/2 the size of the coefficient grid.  Our coefficient grid sizes range from
64x256 grid points at the lowest values of Ra to 768x3072 grid points at Ra $\geq 10^{7}$.

\section{Results}
\refstepcounter{section}
\label{sec:results}

The efficiency of convection is quantified by the Nusselt number.  
While the Nusselt number is well-defined in \RB convection
as the amount of total flux divided by the steady-state background conductive flux 
\cite{johnston&doering2009, otero&all2002},
a well-defined Nusselt number is more elusive in stratified convection.  A traditional definition of the Nusselt
number in stratified convection is \cite{graham1975,hurlburt&all1984}
\begin{equation}
N \equiv \frac{F_{\text{conv, z}} + F_{\text{rad, z}} - F_A}{F_{\text{ref}} - F_A},
\label{eqn:nusselt}
\end{equation}
where $F_{\text{conv, z}}$ and $F_{\text{rad, z}}$ are the z-components of $\bm{F}_{\text{conv}}$ and $\bm{F}_{\text{rad}}$,
respectively.  $F_A$ is the adiabatic conductive flux, defined as $F_A = -\kappa \partial_z T_{\text{ad}}$.  For an
atmosphere in hydrostatic equilibrium, such as a polytrope, $\partial_z T_{\text{ad}} \equiv - g / c_{P}$, and thus
$F_A = \kappa g / c_{P}$.  $F_{\text{ref}} = \Delta T / L_z$ is the conductive flux of a linear profile connecting the upper
and lower plates, where $\Delta T = T_{u} - T_{\ell}$.

Such a definition of the Nusselt number is general to both stratified and \RB convection.  Convection works to
suppress entropy stratification and create isentropic atmospheres.  Under the Boussinesq approximation where
density variations are ignored, entropy stratification is directly proportional to temperature stratification,
such that $\grad S \rightarrow 0$ only when $\grad T \rightarrow 0$.  Thus, for \RB convection, 
$\grad T_{\text{ad}} \equiv 0$ and the familiar form of $N$ is retrieved.  In the case of stratified convection,
as $\epsilon \rightarrow m_{ad} + 1$, $\grad P \propto g \rightarrow 0$ and
the resulting $\grad T_{\text{ad}} \rightarrow 0$.  In such a case, $F_A \rightarrow 0$ and the familiar
definition of the \RB nusselt number is appropriate to use, which explains why convection carries all of the
atmosphereic flux in such a case \cite{brandenburg&all2005}. However, for any given values of $\epsilon$, including
the very small values used in this work, Eq. \ref{eqn:nusselt} is the proper non-dimensional definition
of the Nusselt number.

We solved initial value problems which started in hydrostatic equilibrium and experienced infinitesimal kicks
in $T_1$ compared to $\epsilon$.  Solutions were time-evolved until a long-time average of $N$ showed little
dependence on height. At
high values of $\epsilon$, shock systems form in the upper atmosphere near downflow lanes 
(see e.g. Fig. \ref{fig:entropy_snapshots}a) and propagate towards upflow lanes.  Such systems were reported in
both two \cite{cattaneo&all1990} and three \cite{malagoli&all1990} dimensional polytropic simulations previously.
Low mach number flows, such as those in an $\epsilon = 10^{-4}$ atmosphere (e.g. Fig. \ref{fig:entropy_snapshots}b)
have similar bulk thermodynamic structure but lack the complicating dynamics of shock heating. As Ra is
increased to very large values (e.g. Fig. \ref{fig:entropy_snapshots}c), thermodynamic structures no longer span
the vertical extent of the domain but instead break up into small packets which traverse through the domain many
times before diffusing.  The complicated nature of high Ra dynamics, especially in the low Ma regime where
shocks are absent, has barred us from sufficiently converging any solutions in the regime of $Ra > 10^7$.

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/snapshots_fig.png}
\caption{Characteristic entropy fields are shown. The time- and horizontally-
averaged profile is removed in all cases.  At high
$\epsilon$ (a), shock systems form near the upper downflow lanes and propel shock-heated material deep within
the atmosphere at sufficiently high Ra.  At low $\epsilon$ but at the same Ra (b), shock systems are absent from
the system, but otherwise the dynamics are similar.  As Ra is increased (c), downflow lanes no longer span
the entirety of the domain and individual cold, small blobs are responsible for carrying the flux downward.
\label{fig:entropy_snapshots} }
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/fluxes_fig.png}
\caption{Flux profiles for low (top) and high (bottom) Mach number flows.  
\label{fig:flux_profiles} }
\end{figure}

At low Rayleigh number, diffusivities are high and the flows are very laminar.  Such flows often achieve a
steady state and have a well-defined Nusselt number which is independent of time.  However, as the Rayleigh
number increases, the flows become increasingly time-dependent.  Even steady structures such as solid
``rolls'' like those pictured in Fig. \ref{fig:entropy_snapshots} have highly time-dependent Nusselt numbers.
This is, in part, due to the fact that cold downdrafts floating to the bottom of the domain can be entrained
by upflows, or warm risen parcels can be entrainedi n the intense cold downdrafts.  Such events reverse the
preferred direction of flux in the system, and even let the Nusselt number become negative for short periods of
time.  As a result, it is necessary to take a long time average of the fluxes
before calculating the Nusselt number at higher Rayleigh number. (IS THIS USEFUL?)

%
%\begin{figure}[t]
%\includegraphics[width=3.4375in]{./figs/nu_v_time.png}
%\caption{The evolution of the Nusselt number is shown at low ($10^2$) and high ($10^7$) Rayleigh number and at
%$\epsilon = 10^{-4}$.  At low Rayleigh number, the system is able to settle into a time invariant solution. As
%the Rayleigh number is raised, the thermodynamic structure become increasingly complex and time variant, and a
%time-average of the Nusselt number is required to obtain a sensible mean.
%\label{fig:nu_v_time} }
%\end{figure}

@@

\section{Discussion}
\refstepcounter{section}
\label{sec:discussion}

\subsection{acknowledgements}
This work was supported by the CU/NSO Hale Graduate Fellowship and Juri's allocation and Ben's allocation.
We thank Axel Brandenburg, Mark Rast, and Jeff Oishi for many useful discussions.
